\documentclass[12pt,twoside]{report}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{polski}

\usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{wrapfig}

\usepackage{textcomp}
\usepackage{amsmath}
	\numberwithin{equation}{subsection}
\usepackage{caption}
\usepackage{subcaption}

\setlength\parindent{0pt}
\usepackage{sectsty,textcase}
\allsectionsfont{\MakeTextUppercase}


\usepackage[a4paper,width=150mm,top=25mm,bottom=25mm,bindingoffset=6mm]{geometry}
\usepackage[english]{babel}
\usepackage[nottoc]{tocbibind}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%TABLE OF CONTENTS LETTERS CHANGE
\usepackage{regexpatch}
\makeatletter
\xpatchcmd*{\@sect}{\fi#7}{\fi\@nameuse{format#1}{#7}}{}{}
%%% for sections and subsections we want uppercase
\protected\def\formatsection{\MakeUppercase}
\protected\def\formatsubsection{\MakeUppercase}

%%% the other titles are left unchanged
\let\formatsubsubsection\@firstofone
\let\formatparagraph\@firstofone
\let\formatsubparagraph\@firstofone

%%% the following is necessary only if hyperref is used
\AtBeginDocument{%
  \pdfstringdefDisableCommands{%
    \let\formatsection\@firstofone
    \let\formatsubsection\@firstofone
  }%
}
\makeatother
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{hyperref}

 
\urlstyle{same}

\usepackage{fancyhdr}
	\pagestyle{fancy}
	\setlength{\headheight}{28pt}
	\fancyhead{}
	\fancyhead[RO,LE]{Chapter \thechapter}
	\fancyfoot{}
	\fancyfoot[CO,CE]{\thepage}
\usepackage{csquotes}
\usepackage[backend=biber]{biblatex}
\addbibresource{ref.bib}

\begin{document}

\graphicspath{ {images/} }
\input{title.tex}


\chapter*{\textbf{ABSTRACT}}
In this thesis the extensive study of possible and surly optimal materials for Quantum Dot Solar Cells (QDSCs) will be provided to the reader. One will have the opportunity to develop a rather current image of the necessary parts in their architecture which will be supported with an abundant description of the important aspects in engineering a photovoltaic device. With an introduction of its kind we will try to convey a basic but sufficient knowledge of standard terms, light with matter interaction, light spectrum analysis, quantum dots description with their behaviour and a photovoltaic device operation theory with certainly needed quantities that one has to find in order to properly describe a solar cell. With the objective of creating a possibly competitive Quantum Dot Sensitized Solar Cell(QDSSC) the description of methods that we used will be included with a related to it characteristics. One will also be able to use this paper as a review of today's development phase and current technological state of the other scientific groups all around the world.  After a successful development of a solar cell, the analysis and comparison will definitely be provided.

\chapter*{STRESZCZENIE}

W tej pracy skupimy się na badaniu możliwych, a także optymalnych materiałów pod ogniwa słoneczne bazujące na kropkach kwantowych. Możliwe będzie wyrobienie sobie obecnego obrazu potrzebnych w ich budowie materiałów oraz zapoznanie się z wyczerpującym opisem projektowania tychże urządzeń. Wraz ze wstępem przedstawione zostaną wystarczające podstawy oddziaływania światła z materią, analizy spektralnej, opisu kropek kwantowych, działania urządzeń fotowoltaicznych, a także oznaczenia używane w pracy. Wraz z celem stworzenia możliwe konkurencyjnego urządzenia pokazany zostanie również opis użytych metod. Dodatkowo, możliwe będzie również traktowanie pracy jako krótki przegląd obecnego rozwoju technologii zwiazanych QDSSC na całym świecie. Po wykonaniu urządzenia przeprowadzona zostanie również analiza i porównanie wyników.
 
\chapter*{DEDICATION}
I would like to dedicate ...

\chapter*{DECLARATION}


I hereby declare that the present bachelor's thesis was composed by myself and that the work contained herein is my own. I also confirm that I have only used the specified resources. All formulations and concepts taken verbatim or in substance from printed or unprinted material or from the Internet have been cited according to the rules of good
scientific practice and indicated by footnotes or other exact references to the original source.

\vline

\noindent The present thesis has not been submitted to another university for the award of an academic
degree in this form. This thesis has been submitted in printed and electronic form. I hereby
confirm that the content of the digital version is the same as in the printed version.
I understand that the provision of incorrect information may have legal consequences.
\vfill

(Signature)\hfill (Place, Date)
\vspace{8.5cm}


\chapter*{ACKNOWLEDGEMENTS}
Thanks 

\tableofcontents
\listoffigures 
\listoftables

\input{chapters/ch1}

\input{chapters/ch2}

\input{chapters/ch3}

\input{chapters/ch4}

\input{chapters/ch5}

\input{chapters/ch6}


\addcontentsline{toc}{chapter}{BIBLIOGRAPHY}
\printbibliography

\end{document}