As in the photovoltaic physics we are constantly struggling with the light itself, we should know what the light actually is and how it interacts with matter in many, rather curious and different ways. Why is that so that matter looks the way it does and what of its properties can we control? In this chapter we will embrace the phenomena just to create an image of what we are dealing with. 

\subsection{ELECTROMAGNETIC FIELD}

Before we actually begin we need to state some classic information about
the physics of electric charges. The electromagnetic field is
represented by two, generally complex, vectors, even though the physical
result that we are expecting is ought to be real. Those vectors are
\textbf{E} -- \emph{electric field} and \textbf{B} -- \emph{magnetic
induction}. The properties of those fields are of course described by
the \emph{Maxwell's equations}. For them we shall also introduce two
more important quantities \(\rho\) -- \emph{the electric charge} density
and \textbf{j} -- \emph{electric current density} vector.
We can define them in this way:
\begin{equation}
e = \int\rho dV
\end{equation}

\begin{equation}
I = \int_{S}^{}\mathbf{j \cdot dS}
\end{equation}

\noindent Where I is electric current.

\noindent The four Maxwell equations in differential form are:
\begin{equation}
\nabla \times \mathbf{E} = -\frac{\partial\mathbf{B}}{\partial t}\mathbf{\rightarrow}
\emph{Faraday's induction law}
\end{equation}

\begin{equation}
\nabla \times \mathbf{B}=\mu_{0}\left( \mathbf{j +}\epsilon_{0}\frac{\partial\mathbf{E}}{\partial t} \right) \rightarrow
\emph{Ampere's circuital law}
\end{equation}

\begin{equation}
\nabla \cdot \mathbf{E}=\frac{\rho}{\epsilon_{0}}\mathbf{\rightarrow}
\emph{Gauss's law}
\end{equation}

\begin{equation}
\nabla \cdot \mathbf{B} =  0 \rightarrow \emph{Gauss's law for
magnetism}
\end{equation}

To freely describe the properties of the fields interacting
macroscopically with material objects we can also introduce
standard auxiliary fields with polarization and magnetisation of a
macroscopic medium. Those vectors are \textbf{D --} \emph{the electric
displacement} and \textbf{H} -- \emph{the magnetic vector}. From Gauss's
law for magnetism there is a straight implication that no magnetics
monopoles exist and Gauss's law may be also treated as electric charge
density definition.

\begin{equation}
\mathbf{D}\left( \mathbf{r,}t \right) = \epsilon_{0}\mathbf{E}\left( \mathbf{r,}t \right) + \mathbf{P(r,}t)
\end{equation}

\begin{equation}
\mathbf{H}\left( \mathbf{r,}\text{\ t} \right) = \frac{1}{\mu_{0}}\mathbf{B}\left( \mathbf{r,\ }t \right) - M(\mathbf{r,\ }t)
\end{equation}

\noindent Where \textbf{P} is a \emph{polarization} \emph{vector} and \textbf{M}
is \emph{magnetization vector}.

\noindent And with them our former equations change to:

\begin{equation}
\nabla \times \mathbf{E} = -\frac{\partial\mathbf{B}}{\partial t}\mathbf{\rightarrow}
\emph{Faraday's induction law}
\label{Faraday}
\end{equation}

\begin{equation}
\nabla \times \mathbf{H =}\left( \mathbf{j +}\frac{\partial\mathbf{D}}{\partial t} \right) \rightarrow
\emph{Ampere's circuital law}
\label{Ampere}
\end{equation}

\begin{equation}
\nabla \cdot \mathbf{D =}\rho\mathbf{\rightarrow} \emph{Gauss's
law}
\end{equation}

\begin{equation}
\nabla \cdot \mathbf{B = \ 0 \rightarrow} \emph{Gauss's law for
magnetism}
\end{equation}

If we put divergence on the Ampere's law, we can then place Gauss's
theorem in the equation because of the exchangeability of partial
derivatives and from that we can simply derive so called equation for
\emph{charge conservation:}

\begin{equation}
\frac{\partial\rho}{\partial t} + \nabla \cdot \mathbf{j = 0}
\end{equation}

The field is said to be static if all quantities are independent of time
and, of course by itself, no currents are present. This is the special case, but we
cannot be so lucky every time. Optical fields are usually sources of rapid time variety, but one may deal with it thanks to the
possibility to average the field over macroscopic time interval which is
mostly the case for photovoltaic needs, where for example the light
source is at large distance.

Relations for substances under influence of those fields can be considerably
complicated. There is a special case that can make life easier as well.
If the material is \emph{isotropic} (all its properties are identical in
every direction) they take a simple form of:

\begin{equation}
\mathbf{j} = \sigma\mathbf{E \rightarrow} Ohm's law
\end{equation}

\begin{equation}
\mathbf{D =}\epsilon\mathbf{E}
\end{equation}

\begin{equation}
\mathbf{B =}\mu\mathbf{H}
\end{equation}

Here \(\sigma\) is called \emph{conductivity}, \(\epsilon\) is a
\emph{dielectric constant} and \(\mu\) is \emph{magnetic permeability.}
Normally, all of those are tensors. In the case of scalar conductivity
we can separate macroscopic media in three different categories:
conductors, semiconductors and isolators. The same goes for magnetic
permeability. With \(\mu < 1\) the substance is said to be diamagnetic,
\(\mu > 1\) paramagnetic and so with \(\mu \gg 1\) ferromagnetic.
Obviously this description is rather intuitive and treated as a general
theory. For example for exceptionally strong fields the area of
non-linear optics is needed to be got into which provides higher power
terms of fields in the above equations. Also, the case where we need to
include relativistic effects by extracting previous values of E acting
on charges is not included as well. Of course, considering electromagnetic fields, we need to include the boundary conditions, yet they are not necessary for now. The information will be expanded later when needed, but if the reader wants to really expand following discussion understanding, it can be done via \cite{Born1999} \cite{Jackson}.


\subsection{ENERGY OF ELECTROMAGNETIC FIELD, THE POYNTING VECTOR}

One might say that light is a transporter of energy itself, and the light intensity is easily interpreted as the energy flux of the electromagnetic field. All of the following equations can be beautifully derived via Lagrangian mathematics but we will just provide quick view derived from the Maxwell's equations. 

From both Maxwell equations connecting rotations Eq.\ref{Ampere} and Eq.\ref{Faraday}(they will be provided in \textbf{CGI} units now to show that we can use both) we can get:
\begin{equation}
\mathbf{E}\cdot \nabla \times \mathbf{H} - \mathbf{H} \times \nabla \times \mathbf{E} = \frac{4\pi}{c}\mathbf{j}\cdot \mathbf{E} + \frac{1}{c}\mathbf{E} \cdot \frac{\partial \mathbf{D}}{\partial t} + \frac{1}{c} \mathbf{H} \cdot \frac{\partial \mathbf{B}}{\partial t}
\end{equation}

Then after using vector identities, integrating around some volume, using Gauss's theorem and introducing unit vector normal to the plane \textbf{n} we get:
$$
\frac{1}{4\pi} \int (\mathbf{E} \cdot  \frac{\partial \mathbf{D}}{\partial t}) + (\mathbf{H} \cdot \frac{\partial \mathbf{B}}{\partial t})dV + \int \mathbf{j} \cdot \mathbf{E} dV + \frac{c}{4\pi }\int  (\mathbf{E}\times \mathbf{H}) \cdot \mathbf{n} dS = 0
$$
Where the medium is thought to be isotropic. After taking material equations directly and introducing:
\begin{equation}
w_e = \frac{1}{8\pi}\mathbf{E} \cdot \mathbf{D}
\end{equation}

\begin{equation}
w_m = \frac{1}{8\pi}\mathbf{H} \cdot \mathbf{B}
\end{equation}

and 
\begin{equation}
W = \int (w_e + w_m) dV
\end{equation}

We now have:



$$
\frac{dW}{dt} + \int \mathbf{j} \cdot \mathbf{E}dV + \frac{c}{4\pi } \int  ( \mathbf{E} \times \mathbf{H} )  \cdot \mathbf{n} dS = 0
$$


And W represents total energy contained in the arbitrary volume so therefore $w_e$ and $w_m$ are electric and magnetic energy densities respectively. From that after introducing total work needed to displace charges A we get:

$$
\frac{dW}{dt} = -\frac{\delta A}{\delta t} - Q - \int \mathbf{S} \cdot \mathbf{n} dS
$$

where Q is total charge and S is a Poynting vector interpreted as a density of energy flow and is equal:

\begin{equation}
\mathbf{S} = \frac{c}{4\pi}(\mathbf{E} \times \mathbf{H})
\end{equation}

